Formal verification of train route planning

### 2025-06-27 paper/main.tex
Experiences

\paragraph{Optimisations. } We apply some optimisations on the orders. For instance, we remove orders that do not alternate: $\su{d}{\vec{b}} \cdot \su{d}{\vec{b}} \cdot P$ by $\su{d}{\vec{b} \cdot \vec{b'}} \cdot P$. In the same way,  we remove empty lists, singleton lists: if $Len(\vec{b}) \leq 1$, we replace $\su{d}{\vec{b}} \cdot P$ by $P$. We have few more heuristics that we do not show here due to lack of space.

\paragraph{Experiments}  Parler des expériences

@@

Our implementation, including both the TLA model and the Python composition is available on...\todo{Donner le lien vers github ? }.

>>>>

\paragraph{Optimisations.} We apply some optimisations on the orders. For instance, we remove orders that do not alternate: $\su{d}{\vec{b}} \cdot \su{d}{\vec{b}} \cdot P$ by $\su{d}{\vec{b} \cdot \vec{b'}} \cdot P$. In the same way,  we remove empty lists, singleton lists: if $Len(\vec{b}) \leq 1$, we replace $\su{d}{\vec{b}} \cdot P$ by $P$. We have few more heuristics that we do not show here due to lack of space.

\paragraph{Experiments.}
We implemented a set of Python scripts which perform and model check the composition. The general architecture of our scripts is shown in Figure~\ref{fig:toolchain}. We ran this composition toolchain\footnote{Experiments were run on an earlier version of composition. Slight modifications have been introduced in the presentation above to ease the presentation.} on a cluster. Experiments were run on 8 nodes equipped with Intel Xeon Gold 5220 processors, each having 18 cores at 2.2GHz. It took less than 24h to verify all compositions of two safe steps.

@@

Our implementation, including both the TLA model and the Python composition is available on \url{https://github.com/LucasVillaume/stage-train}.\todo{Remplacer Zenodo si on a le temps}.
